# Early Medical Years {-}

## Transitioning to Rochester {-}

### Very general guidance on finding a place to live {-}

Medical school is a sharp transition in workflow, that requires a lot of your time and energy. As such, even generally short commutes or coordinating a complex parking situation can get to be a thorn in your side on heavy studying days. Getting some extra sleep or being able to zip out to the library when you really need piece and quiet is a real plus if you're pulling late nights.

Because of this, it is generally recommended to find a place close to the University for at least your first year in the program. Considering you'll be spending 7-9 years here, using the first year to hammer down your medical school workflow and get a feel for Rochester is a generally good investment of your time. For single people, this tends to manifest as getting a room/splitting a house in the White Coat or accompanying neighborhoods or getting a room in Goler House. For couples, this tend to be getting an apartment at University Apartments or one of the many apartment complexes nearby.

This one year spent getting your footing can really pay off in the long run. Even if you end up wanting to move farther from the University, the one year spent getting your footing and exploring the variety of neighborhoods in Rochester allows you to get the most out of your housing situation in the back 6-8 years without putting to much stress on you at the transition point.

## Advice for Courses

### HSF

### MTC

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
